---
title: 'R markdown Advanced'
output: 
  html_document: 
    df_print: kable
    number_sections: yes
    toc: yes
editor_options: 
  chunk_output_type: console
header-includes:
   - \usepackage{amssymb}
   - \usepackage{amsmath}
---

For source code see [github page](https://github.com/strnda/tools/blob/master/adv_mkdn/avd.Rmd).    

# R Markdown with other languages {.tabset}

## python

### Setup 
```{r}
if (!require(package = reticulate)) {
  
  install.packages(pkgs = "reticulate")
}
```

### python variable in R
```{python}
x = .1 + .1 + .1

print(x)
```

```{r}
py$x
```


### vice versa
```{r}
x <- rnorm(n = 10)
```

```{python}
print(r.x)
```


## bash
see [link](https://github.com/strnda/tools/blob/master/txt/linux)
```{bash}
echo 'Hello Bash!'
ls -la

```

# HTML widgets {.tabset}

Install the packages if not present 
```{r, message = FALSE, warning = FALSE, cache = FALSE}

lop <- c('broom',
         'dplyr',
         'leaflet',
         'dygraphs',
         'ggplot2',
         'plotly', 
         'highcharter', 
         'visNetwork', 
         'networkD3', 
         'DT', 
         'DiagrammeR')

to.instal <- lop[which(x = !lop %in% installed.packages()[,'Package'])]

if(length(x = to.instal) != 0) {
  
  install.packages(pkgs = to.instal)
}

aux <- lapply(X = lop, 
       FUN = library, character.only = T)

rm(list = 'aux')
```


## leaflet
```{r}
data(quakes)

head(quakes)

leaflet(data = quakes[1:20,]) %>% 
  addTiles() %>%
  addMarkers(lng = ~long, 
             lat = ~lat, 
             popup = ~as.character(x = mag), 
             label = ~as.character(x = mag))

```

## dygraphs
```{r}
dygraph(data = nhtemp, 
        main = 'New Haven Temperatures') %>% 
  dyRangeSelector(dateWindow = c('1920-01-01', 
                                 '1960-01-01'))
```

## plotly {.tabset}
### ggplot2 with plotly
```{r}
p <- ggplot(data = diamonds, 
            mapping = aes(x = cut, 
                          fill = clarity)) +
            geom_bar(position = 'dodge')

ggplotly(p = p)
```

### pure plotly
```{r}
plot_ly(z = ~volcano, 
        type = 'heatmap')

plot_ly(z = ~volcano, 
        type = 'surface')
```

## highcharter
```{r, warning = FALSE}
data(diamonds)

set.seed(seed = 123)
data <- sample_n(tbl = diamonds, 
                 size = 300)

modlss <- loess(formula = price ~ carat, 
                data = data)
fit <- arrange(.data = augment(x = modlss), 
               carat)

highchart() %>%
  hc_add_series(data = data, 
                type = 'scatter',
                hcaes(x = carat, 
                      y = price, 
                      size = depth, 
                      group = cut)) %>%
  hc_add_series(data = fit, 
                type = 'line', 
                hcaes(x = carat, 
                      y = .fitted),
                name = 'Fit', 
                id = 'fit') %>%
  hc_add_series(data = fit, 
                type = 'arearange',
                hcaes(x = carat, 
                      low = .fitted - 2*.se.fit,
                      high = .fitted + 2*.se.fit),
                linkedTo = 'fit')
```

## visNetwork
```{r}
nodes <- data.frame(id = 1:6, 
                    title = paste("node", 1:6), 
                    shape = c("dot", "square"),
                    size = 10:15, 
                    color = c("blue", "red"))
edges <- data.frame(from = 1:5, 
                    to = c(5, 4, 6, 3, 3))
head(x = nodes)

visNetwork(nodes = nodes, 
           edges = edges)
```


```{r}
nodes <- data.frame(id = 1:10, 
                    label = paste("Node", 1:10),
                    group = c("GrA", "GrB"),
                    value = 1:10, 
                    shape = c("square", "triangle", "box", "circle", "dot", "star",
                              "ellipse", "database", "text", "diamond"),
                    title = paste0("<p><b>", 1:10,"</b><br>Node !</p>"), 
                    color = c("darkred", "grey", "orange", "darkblue", "purple"),
                    shadow = c(FALSE, TRUE, FALSE, TRUE, TRUE)) 

edges <- data.frame(from = sample(1:10,8), to = sample(1:10, 8),
                    label = paste("Edge", 1:8), 
                    length = c(100,500), 
                    arrows = c("to", "from", "middle", "middle;to"),
                    dashes = c(TRUE, FALSE),  
                    title = paste("Edge", 1:8), 
                    smooth = c(FALSE, TRUE),  
                    shadow = c(FALSE, TRUE, FALSE, TRUE)) 

visNetwork(nodes = nodes, edges = edges) %>%
  visOptions(highlightNearest = TRUE,
             nodesIdSelection = TRUE)
```

## DataTables
```{r}
datatable(data = iris, 
          options = list(pageLength = 10),
          class = 'cell-border stripe',
          editable = 'cell')
```

# \( \LaTeX \)

The three-parameter Generalizeed Pareto distribution (GPD) is formulated as

\begin{equation}
    f(x) = \alpha^{-1}e^{-(1 - \kappa)y}, \quad y = \begin{cases} -\kappa^{-1}\log \Big[ 1 - \frac{\kappa(x - \xi)}{\alpha} \Big], & \kappa \neq 0,\\\frac{(x - \xi)}{\alpha}, & \kappa = 0.\end{cases}
\end{equation}

where $\xi \in  R$ is location, $\alpha > 0$ scale and $\kappa \in  R$ shape parameter with range of $x$: $\xi \leq x \leq \xi + \alpha/\kappa$ if $\kappa > 0$ and $\xi \leq x \leq \infty$ if $\kappa \leq 0$. 